---
title: "R Notebook"
output: html_notebook
---

a. Construct and store a 4 × 2 matrix that’s filled row-wise with the values 4.3, 3.1, 8.2, 8.2, 3.2, 0.9, 1.6, and 6.5, in that order.
```{r}
mat <- matrix(data=  c(4.3, 3.1, 8.2, 8.2, 3.2, 0.9, 1.6, 6.5),
                       nrow=4, ncol=2, byrow=T)

```

b. Confirm the dimensions of the matrix from (a) are 3 × 2 if you remove any one row.
```{r}
dim(mat[-4,])
```

c. Overwrite the second column of the matrix from (a) with that same column sorted from smallest to largest.
```{r}
mat[,2] <- sort(mat[,2])
```

d. What does R return if you delete the fourth row and the first column from (c)? Use matrix to ensure the result is a single-column matrix, rather than a vector.
```{r}
mat[-4,-1]
```

e. Store the bottom four elements of (c) as a new 2 × 2 matrix.
```{r}
new_mat <- mat[3:4,]
```

f. Overwrite, in this order, the elements of (c) at positions (4,2),
(1,2), (4,1), and (1,1) with $−\frac{1}{2}$ of the two values on the diagonal of (e).


```{r}
mat[c(4,1), c(2,1)] <- -1/2 * diag(new_mat)
mat
```
