---
title: "R Notebook"
output: html_notebook
---

a. Create and store a three-dimensional array with six layers of a
4 × 2 matrix, filled with a decreasing sequence of values between
4.8 and 0.1 of the appropriate length.
```{r}
t_array <- array(data=seq(4.8,0.1,length.out=48), dim=c(4,2,6))
t_array
```

b. Extract and store as a new object the fourth- and first-row elements, in that order, of the second column only of all layers
of (a).
```{r}
fourth_and_first <- t_array[c(1,4),2,]
fourth_and_first
```

c. Use a fourfold repetition of the second row of the matrix formed
in (b) to fill a new array of dimensions 2 × 2 × 2 × 3.
```{r}
new_array <- array(data=rep(fourth_and_first[1,],4),
                   dim=c(2,2,2,3))
new_array
```

d. Create a new array comprised of the results of deleting the sixth
layer of (a).
```{r}
without_array <- t_array[,,-6]
without_array
```

e. Overwrite the second and fourth row elements of the second
column of layers 1, 3, and 5 of (d) with −99.
```{r}
without_array[c(2,4), 2, c(1,3,5)] <- -99 
without_array
```

