---
title: "R Notebook"
output: html_notebook
---
Store the following vector of 15 values as an object in your
workspace: c(6,9,7,3,6,7,9,6,3,6,6,7,1,9,1). Identify the following elements:
i. Those equal to 6
```{r}
myvec <- c(6,9,7,3,6,7,9,6,3,6,6,7,1,9,1)
myvec[myvec == 6]
```


ii. Those greater than or equal to 6
```{r}
myvec[myvec >= 6]
```


iii. Those less than 6 + 2
```{r}
myvec[myvec < 6] + 2
```


iv. Those not equal to 6
```{r}
myvec[myvec != 6]
```


b. Create a new vector from the one used in (a) by deleting its
first three elements. With this new vector, fill a 2 × 2 × 3 array.
```{r}
new_array <- array(data=myvec[-(1:3)], dim=c(2,2,3))
new_array
```


Examine the array for the following entries:
i. Those less than or equal to 6 divided by 2, plus 4
```{r}
new_array <= 6/2 + 4

```


ii. Those less than or equal to 6 divided by 2, plus 4, after
increasing every element in the array by 2
```{r}
new_array  + 2 <= 6/2+4
```


c. Confirm the specific locations of elements equal to 0 in the
10 × 10 identity matrix I10 (see Section 3.3).
```{r}
logical_matrix <- diag(10) == 0
```



d. Check whether any of the values of the logical arrays created in
(b) are TRUE. If they are, check whether they are all TRUE.
```{r}
any(new_array)
all(new_array)

```


e. By extracting the diagonal elements of the logical matrix created
in (c), use any to confirm there are no TRUE entries.
```{r}
any(diag(logical_matrix))

```

