---
title: "R Notebook"
output: html_notebook
---
a. Store the vector c(7,1,7,10,5,9,10,3,10,8) as foo. Identify the
elements greater than 5 OR equal to 2.
```{r}
foo <- c(7,1,7,10,5,9,10,3,10,8)
foo > 5 | foo == 2
```

b. Store the vector c(8,8,4,4,5,1,5,6,6,8) as bar. Identify the elements less than or equal to 6 AND not equal to 4.
```{r}
bar <- c(8,8,4,4,5,1,5,6,6,8)
bar <= 6 & bar != 4

```

c. Identify the elements that satisfy (a) in foo AND satisfy (b) in bar.
```{r}
a <- foo > 5 | foo == 2
b <- bar <= 6 & bar != 4
a & b
```

d. Store a third vector called baz that is equal to the element-wise
sum of foo and bar. Determine the following:
i. The elements of baz greater than or equal to 14 but not equal to 15
```{r}
baz <- foo + bar
baz >= 14 & baz != 15
```


ii. The elements of the vector obtained via an element-wise
division of baz by foo that are greater than 4 OR less than or
equal to 2
```{r}
newvec <- baz/foo
newvec > 4 | newvec <= 2
```

e. Confirm that using the long version in all of the preceding
exercises performs only the first comparison (that is, the results
each match the first entries of the previously obtained vectors)
```{r}
(foo>5)||(foo==2)
(bar<=6)&&(bar!=4)
((foo>5)||(foo==2))&&((bar<=6)&&(bar!=4))
(baz>=14)&&(baz!=15)
(baz/foo>4)||(baz/foo<=2)

```

