---
title: "R Notebook"
output: html_notebook
---
a. Re-create exactly the following output:
"The quick brown fox
    jumped over
        the lazy dogs"
```{r}
cat("The quick fox\n\tjumped over\n\t\tthe lazy dogs")
```

b. Suppose you’ve stored the values num1 <- 4 and num2 <- 0.75.
Write a line of R code that returns the following string:
[1] "The result of multiplying 4 by 0.75 is 3"
Make sure your code produces a string with the correct
multiplication result for any two numbers stored as num1 and num2.
```{r}
num1 <- 4
num2 <- 0.5
cat("The result of multiplying", num1, "by", num2, "is 3")
```

c. On my local machine, the directory for my work on this book is
specified in R as "/Users/tdavies/Documents/RBook/". Imagine it is
your machine—write a line of code that replaces tdavies in this
string with your first initial and surname.
78 Chapter 4
```{r}
str <- "/Users/tdavies/Documents/RBook/"
sub("tdavies", "VCaetano", str)
```

d. In Section 4.2.4, you stored the following string:
R> bar <- "How much wood could a woodchuck chuck"
i. Store a new string by gluing onto bar the words
"if a woodchuck could chuck wood".
```{r}
bar <- "How much wood could a woodchuck chuck"
bar <- sub(bar , "if a woodchuck could chuck wood", bar)
bar
```

ii. In the result of (i), replace all instances of wood with metal.
```{r}
gsub("wood", "metal", bar)
```

e. Store the string "Two 6-packs for $12.99". Then do the following:
i. Use a check for equality to confirm that the substring
beginning with character 5 and ending with character 10
is "6-pack".
```{r}
promo <-  "Two 6-packs for $12.99"
substring(promo, 5, 10) == "6-pack"
```

ii. Make it a better deal by changing the price to $10.99.
```{r}
sub("12.99", "10.99", promo)
```

