---
title: "R Notebook"
output: html_notebook
---
a. Create and store a sequence of values from 5 to −11 that progresses in steps of 0.3.
```{r}
sequence = seq(from=5, to=(-11), by=-0.3)
sequence
```


b. Overwrite the object from (a) using the same sequence with the
order reversed.
```{r}
sequence = sort(sequence)
sequence

```


c. Repeat the vector c(-1,3,-5,7,-9) twice, with each element
repeated 10 times, and store the result. Display the result sorted
from largest to smallest.
```{r}
vec = rep(x=c(-1,3,-5,7,-9), times=2, each=10)
vec
```


d. Create and store a vector that contains, in any configuration, the
following:
i. A sequence of integers from 6 to 12 (inclusive)
ii. A threefold repetition of the value 5.3
iii. The number −3
iv. A sequence of nine values starting at 102 and ending at the
number that is the total length of the vector created in (c)
```{r}
i = seq(6,12)
ii = rep(5.3, 3)
iii = -3
iv = seq(from=102, to=length(vec), length.out=9)

newvec = c(i,ii,iii,iv)
```


e. Confirm that the length of the vector created in (d) is 20.

```{r}
length(newvec)
```

