---
title: "2-5"
output: html_notebook
---

a. Convert the vector c(2,0.5,1,2,0.5,1,2,0.5,1) to a vector of only
1s, using a vector of length 3.
```{r}
vec <-  c(2,0.5,1,2,0.5,1,2,0.5,1)
vec <-  vec * c(0.5,2,1) 
vec
```

b. The conversion from a temperature measurement in degrees
Fahrenheit F to Celsius C is performed using the following
equation:
$C = \frac{5}{9}(F − 32)$

Use vector-oriented behavior in R to convert the temperatures 45, 77, 20, 19, 101, 120, and 212 in degrees Fahrenheit to
degrees Celsius.
```{r}
temperatures <-  c(45, 77, 20, 19, 101, 120)
temperatures <-  temperatures - 32
temperatures <-  temperatures * (5/9)
temperatures
```

c. Use the vector c(2,4,6) and the vector c(1,2) in conjunction with
rep and * to produce the vector c(2,4,6,4,8,12).
```{r}
myvec <- c(2,4,6)
myvec <-myvec * rep(c(1,2), each=3)
myvec
```

d. Overwrite the middle four elements of the resulting vector from
(c) with the two recycled values -0.1 and -100, in that order.
```{r}
myvec[-c(1, 6)] = c(-0.1, -100)
myvec
```

