---
title: "2-4"
output: html_notebook
---


a. Create and store a vector that contains the following, in this
order:
– A sequence of length 5 from 3 to 6 (inclusive)
– A twofold repetition of the vector c(2,-5.1,-33)
– The value ${7/42}+2$

```{r}
myve <- c(seq(from=3, to=6, length.out=5), rep(x=c(2,-5.1,-33), times=2), (7/2)+2)
myvec
```


b. Extract the first and last elements of your vector from (a), storing
them as a new object.
```{r}
new_obj <- myvec[c(1, length(myvec))]
new_obj
```


c. Store as a third object the values returned by omitting the first
and last values of your vector from (a).
```{r}
third_obj <-  myvec[-c(1, length(myvec))]
third_obj
```


d. Use only (b) and (c) to reconstruct (a).
```{r}
reconstructed <- c(new_obj[1], third_obj, new_obj[2])
reconstructed
```


e. Overwrite (a) with the same values sorted from smallest to
largest.
```{r}
myvec <-  sort(myvec)
myvec
```


f. Use the colon operator as an index vector to reverse the order
of (e), and confirm this is identical to using sort on (e) with
decreasing=TRUE.
```{r}
myvec_reversed <-  myvec[length(myvec):1]
myvec_reversed 
sort(myvec, decreasing = TRUE)

```


g. Create a vector from (c) that repeats the third element of (c)
three times, the sixth element four times, and the last element once.
```{r}
repeatvector <-  c(rep(third_obj[3], 3), rep(third_obj[6], 4), third_obj[length(third_obj)])
repeatvector
```


h. Create a new vector as a copy of (e) by assigning (e) as is to a
newly named object. Using this new copy of (e), overwrite the
first, the fifth to the seventh (inclusive), and the last element with
the values 99 to 95 (inclusive), respectively.
```{r}
copy <- myvec
copy[c(1, 5:7, length(myvec))] <- 99:95
copy
```

